---
title: "Untitled"
output: html_document
date: "2022-12-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Firstly, set your working directly using the set working director option in the toolbar under 'Session'.

I would set this to a new folder called 'Penguin_project'.

Next, load your libraries 

```{r}
library(palmerpenguins)
library(ggplot2)
library(janitor)
library(dplyr)
```


What we need to do is create a new folder called raw_data inside our project folder manually.

Next, using the following command we are going to save the variable penguins_raw as a .csv file.

```{r}
write.csv(penguins_raw, paste0("data_raw/penguins_raw.csv"))
```

Next, we will make a new function to clean your data, or you can just download and source the function we have used in the function folder, called clean.r

```{r}
cleaning_my_data <- function(penguins_raw){
  penguins_raw %>%
    clean_names () %>%
    remove_empty(c("rows", "cols")) %>%
    select (-starts_with("Delta")) %>%
    select(-comments)
}

```

This next bit of code runs and saves the output of the function in new data set penguins_now_clean

```{r}
penguins_clean <- cleaning_my_data(penguins_raw)
names(penguins_clean)
```


Save the clean data in a new file

```{r}
write.csv(penguins_clean, paste0("data_clean/penguins_clean.csv"))

```


# Running a statistical test: Linear regression model between Culmen length and Culmen depth

```{r}
linear_regression_model <-lm(culmen_length_mm ~ culmen_depth_mm, penguins_clean)
summary(linear_regression_model)
```

 
check assumptions of linear modelling are met
```{r}
plot(linear_regression_model)
```

They are successfully met!

```{r}
ggplot(penguins_clean, aes(x = culmen_length_mm, y = culmen_depth_mm, col = species)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") + labs(title = "Culmen length against depth (mm)", x = "Culmen Length (mm)", y = "Culmen Depth (mm)" )

```

We can turn this into a function:

```{r}
plot_culmen_figure <- function(penguins_clean){
  penguins_clean %>% 
    ggplot(penguins_clean, aes(x = culmen_length_mm, y = culmen_depth_mm, col = species)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") + labs(title = "Culmen length against depth (mm)", x = "Culmen Length (mm)", y = "Culmen Depth (mm)" )
}

```

Next, we must save the data into our 'Figures' folder, we will do so as a 'png' file

```{r}
save_culmen_plot_png <- function(penguins_clean, filename, size, res, scaling){
  agg_png(filename, width = size, 
                    height = size, 
                    units = "cm", 
                    res = res, 
                    scaling = scaling)
  culmen_plot <- plot_flipper_figure(penguins_clean)
  print(culmen_plot)
  dev.off()
}

```


